---
title: 'Unit 09: Programming Practice'
author: "Diogo Viveiros"
date: "2025-10-25"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(dplyr)
library(ggplot2)
```

# Question 3

## Question 3.1

```{r}
 rmystery <- function(n){
  x = runif(n)
  y = runif(n, min=0, max = 1/x)
  data.frame(x=x,y=y)
}
plot(rmystery(100))
```
```{r}
experiment_m <- function(){
  df <- rmystery(100)
  reg <- lm(y ~ x, data = df)
  slope <- coef(reg)[2]
  return(slope)
}

```

```{r}
df_q3 <- data.frame()
```

```{r}
slopes_m <- replicate(10000, experiment_m())
df_q3.1 <- data.frame(slopes = slopes_m)
ggplot(data = df_q3.1, aes(x = slopes)) +
  geom_histogram()
```



## Question 3.3

```{r}
renigma <- function(n){
  x = runif(n)
  y = runif(n, min=0, max = (1-x)^2)
  data.frame(x=x,y=y)
}
plot(renigma(100))
```

```{r}
experiment_e <- function(){
  df <- renigma(100)
  reg <- lm(y ~ x, data = df)
  slope <- coef(reg)[2]
  return(slope)
}
```



```{r}
slopes_e <- replicate(1000, experiment_e())
df_q3.3 <- data.frame(slopes = slopes_e)
ggplot(data = df_q3.3, aes(x = slopes)) +
  geom_histogram()
#hist(slopes_e, breaks = seq(min(slopes_e), max(slopes_e))
```

# Question 4

```{r}
library("fec16")
data("results_house")
data("campaigns")
```

## Question 4.1

```{r}
ggplot(data = results_house, aes(x = general_percent)) +
  geom_histogram()

ggplot(data = campaigns, aes(x = ttl_disb)) +
  geom_histogram(bins = 10)
```

# Questions 4.2/4.3

```{r}
df_q4 <- inner_join(results_house, campaigns, by = "cand_id")
```

## Question 4.4

```{r}
df_q4 <- df_q4 %>%
  mutate(
    candidate_party = case_when(
      party == "DEM" ~ "Democrat",
      party == "REP" ~ "Republican",
      TRUE ~ "Other Party"
    )
  )
```


```{r}
ggplot(data = df_q4, aes(x = ttl_disb, y=general_votes, color = candidate_party)) +
  geom_point() +
  labs(
       x = "Total Disbursement Spending",
       y = "General Votes")+
  ggtitle("Total Spending Disbursement vs General Votes (by Party)") +
  theme(plot.title = element_text(size = 8, face = "bold"))
```


## Question 4.5

## Large-Sample Assumptions

### I.I.D. Data:
The data are independently and identically distributed, as each observation is drawn from the same underlying distribution of candidates. Each candidate’s campaign information is independent of others, meaning that observing one campaign does not directly inform the outcomes of another.

### Existence of the Best Linear Predictor (BLP):
The covariance terms need to be finite, so we should avoid heavy tails. However, based on the distribution observed in Question 4.1, the variable ttl_disb exhibits a very heavy tail. I am going to apply a log transformation ttl_disb in order to smooth out the tails and better satisfy the assumption that there are no infinite variances. There are a lot of values of 0 though, which would be undefined, so we're setting those to 1 with the log1p function.

```{r}
df_q4$log_ttl_disb <- log1p(df_q4$ttl_disb)
ggplot(data = df_q4, aes(x = log_ttl_disb)) +
  geom_histogram()
```

## Uniqueness of the BLP:
There is no perfect collinearity among the regressors to make E[X^TX] invertible. In other words, no explanatory variable can be expressed as a linear combination of the others.
To verify this, a correlation test was conducted between ttl_disb and general_votes, yielding a correlation coefficient of 0.40. This indicates that there is no perfect collinearity, so the log of ttl_disb cannot be written as a linear combination of general_votes, and vice versa.  

```{r}
cor(df_q4$log_ttl_disb, df_q4$general_votes, use = "complete.obs")
```


```{r}
model_1 <- lm(general_votes ~ log_ttl_disb + candidate_party , data = df_q4)
model_1
```

## Question 4.6

```{r}
library(stargazer)
library(sandwich)
library(lmtest)
```
```{r}
robust_se <- coeftest(model_1, vcov = vcovHC(model_1))[, "Std. Error"]
```

```{r, results='asis'}
stargazer(
  model_1,
  type = 'latex',
  title = "Campaign Spending Effects on General Election Votes By Party",
  se = list(robust_se),
  covariate.labels = c(
    "Log Effect of Campaign Spending", 
    "Vote Difference for Other Parties (vs. Democrats)",
    "Vote Difference for Republicans (vs. Democrats)",
    "Baseline Vote Count (Democrat) with No Campaign Spending"
  )
)
```

## Question 4.7



```{r}
model_2 <- lm(general_votes ~ ttl_disb , data = df_q4)
model_2
anova(model_2, model_1, test = "F")
```

## Question 4.8

```{r}
model_3 <- lm(general_votes ~ candidate_party , data = df_q4)
model_3
anova(model_3, model_1, test = "F")
```
```{r}
coeftest(model_1, vcov = vcovHC(model_1))
```

## Office Hours:

If worried about skewness for the statistic you're running, do a log-transform. ( I think in Q4.5?)

Checking for collinearity: run cor(); remove one of the collinear variables and then compare the coefficiencts to check if they're the same after running one and removing the other. 

Last two parts of question 4

Use coeftest(model_x, vcovHC(model_x)) in library(sandwich) and some other library to evaluate robust standard errors. 

Set either Republican or Democrat as the baseline, not the "other" label

Run an f test that compares the last two models you create. 